HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2023-07-04 tmlr_submission/hermes_paper_revision/hermes_paper.tex
add a discussion section

where T denotes the number of available time steps \textcolor{orange}{and $i$ represent a unique identifier summarizing the 4 information $c$, $g$, $m$ and $j$}. The time series $y^{c,g,m,\textcolor{orange}{j}}$ is divided by the deseasonalized signal $\bar{y}^{c,g,m}$ and not $\Tilde{y}^{c,g,m}$ in order to avoid removing the seasonality of all the fashion trend sequences. With this normalizing step, most of the social media bias is removed and the final normalized sequences are expressed in share of category. As an illustration, an example of the normalization process is displayed in Figure~\ref{fig:normalization}. The raw Jersey Top trend for females in China is divided by the deseasonalized global Top trend for females in China.

\begin{figure*}
\centering
  \includegraphics[width=1.\linewidth]{cn_female_top_raw}
  \includegraphics[width=1.\linewidth]{cn_female_top_norm}
\caption{Example of difference between the raw sequence and the normalized one for the Jersey top fashion trend for females in China. In this example, we normalize by the deseasonalized global top fashion trend for females in China. (Top) Time series representing the raw signal of the Jersey top fashion trend for females in China. (Bottom) Time series representing the normalized signal of the Jersey top fashion trend for females in China.}
\label{fig:normalization}
\end{figure*}

@@

\section{Conclusion}
\label{sec:conclusion}
In this paper, we propose  a new hybird model for non stationary time series forecasting. By mixing the performance of local parametric models and a global neural network, \textit{hermes-tbats} clearly outperforms traditional statistical methods and full neural network models on two forecasting tasks. Furthermore, this new model is totally suited to deal with external signals. With a fine pre-processing and a well-designed architecture, the proposed hybrid framework succeeds at leveraging complex extra data and reaches promising accuracy levels. In addition, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided. \textcolor{orange}{We show that it is possible to represent fashion data with time series and introduce statistical models based on social media data. }% Furthermore, with a special focus on the behaviour of influencers, it becomes possible to better anticipate consumers' needs and avoid massive wastes due to overstocks.} 
 By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture. Focusing on the examples with important changes of behaviours, a fine analysis of the impact of the collection of weak signals is the topic of ongoing works. In the same way, an interesting improvement of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses. A perspective is to add a latent discrete label to select dynamically the regime shifts.

>>>>

where T denotes the number of available time steps \textcolor{orange}{and $i$ represent a unique identifier summarizing the 4 information $c$, $g$, $m$ and $j$}. The time series $y^{c,g,m,\textcolor{orange}{j}}$ is divided by the deseasonalized signal $\bar{y}^{c,g,m}$ and not $\Tilde{y}^{c,g,m}$ in order to avoid removing the seasonality of all the fashion trend sequences. With this normalizing step, most of the social media bias is removed and the final normalized sequences are expressed in share of category. As an illustration, an example of the normalization process is displayed in Figure~\ref{fig:normalization}. \textcolor{orange}{In this example, the raw and normalized time series of the Jersey top trend for females in China ($y^{c,g,m,j}$ with $c$=Top,  $g$=Female, $m$=China and  $j$=Jersey top) are presented. So as to compute the normalized signal, the raw time series of the Jersey top trend for females in China is divied by the deseasonalized raw time series representing the global Top trend for female in China.}

\begin{figure*}
\centering
  \includegraphics[width=1.\linewidth]{cn_female_top_raw}
  \includegraphics[width=1.\linewidth]{cn_female_top_norm}
\caption{Example of difference between the raw sequence and the normalized one for the Jersey top fashion trend for females in China. In this example, \textcolor{orange}{the Jersey top fashion raw time series for females in China is normalized} by the deseasonalized global top raw time series for females in China. \textcolor{orange}{The final normalized time series is finally expresssed as a share of the global catagery.} (Top) Time series representing the raw signal of the Jersey top fashion trend for females in China. (Bottom) Time series representing the normalized signal of the Jersey top fashion trend for females in China.}
\label{fig:normalization}
\end{figure*}

@@

\textcolor{orange}{
\subsection{Discussion}
Results of the two previous forecasting tasks illustrate that the proposed hybrid method is a general framework, easily adaptable to different use cases and showing remarkable accuracy results able to compete with other state-of-the-art methods. With its neural network component, it is also able to leverage any kind of external signals, which is starting to become essential in more and more forecasting applications. However, the presented method also shows some weaknesses listed above:
\begin{itemize}
\item With the inclusion of a neural network at the end of the framework, the interpretability of the final prediction of the HERMES method is not possible. For instance, the use of the external signal can not be easily assessed and confidence intervals provided by the statistical predictors are no longer valid when they are used in the hybrid framework. A possible idea already studied in the literature is to reverse the order by using first a neural network to compute a set of parameters that is then used by an interpretable model (see for instance the DeepAR model introduced in \cite{salinas2020}.)
\item The proposed hybrid approach can be computationally long to train and to use in inference. Compared to neural-network-based models, the statistical component of the hybrid model has to be retrained for every new time series. For HERMES variations using a complexe statistical predictor like TBATS, this step can be expensive especially on large datasets.
\item In the Fashion use case, the inclusion and use of the external signals by the HERMES model seems to be sub-optimal. For several examples, the external signal starts to burst but the HERMES approach does not use this information to totally change the first parametric prediction and forecast a burst of the main signal. A possible explanation is that the external signals are relevant only in a few fashion time series. Knowing when and how to use them correctly seems to be too difficult for the corrector component part. An ongoing work is to use several neural network models specialized on different uses of the external signals. Then depending on the past of the time series and the external signals, a hidden state could be used to choose which neural network correctors. In addition to bringing more flexibility on the use of the external signals, this promising work could also improve the interpretability of the final prediction depending at which specialized neural network model was chosen in the final prediction.
\end{itemize}
}
\section{Conclusion}
\label{sec:conclusion}
In this paper, we propose a new hybrid model for non stationary time series forecasting. By mixing the performance of local parametric models and a global neural network, \textit{hermes-tbats} clearly outperforms traditional statistical methods and full neural network models on two forecasting tasks. Furthermore, this new model is totally suited to deal with external signals. With a fine pre-processing and a well-designed architecture, the proposed hybrid framework succeeds at leveraging complex extra data and reaches promising accuracy levels. In addition, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided. \textcolor{orange}{We show that it is possible to represent fashion data with time series and introduce statistical models based on social media data.} By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture. Focusing on the examples with important changes of behaviours, a fine analysis of the impact of the collection of weak signals is the topic of ongoing works. In the same way, an interesting improvement of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses. A perspective is to add a latent discrete label to select dynamically the regime shifts.
